Modal Abstractions for Virtualizing Memory Addresses

### 2023-11-16 programlogic.tex
fig 7 fixed

@@

   \{\begin{array}{l}
   P \ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{iv} \ast \textsf{rflags} \mapsto_{\textsf{r}} \textsf{flgs} \ast \ulcorner (\textsf{rvd + imm} > 0 \lor \textsf{rvd + imm} = 0 ) \urcorner \ast \\

@@

   \end{array} \}_{\textsf{rtv}}

@@

  \{P \ast \mathcal{I}\textsf{ASpace}\ast \mathcal{I}\textsf{ASpace} \ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{iv + x} \ast \ulcorner x = 3 \lor x =4 \urcorner \ast r_d \mapsto_{r}  \textsf{v} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}_{\textsf{rtv}}\;\overline{is}

>>>>

  \makeatletter % allow us to mention @-commands
\def\arcr{\@arraycr}
\makeatother

@@

   \left\{
   \begin{array}{l}
   P \ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{iv} \ast \textsf{rflags} \mapsto_{\textsf{r}} \textsf{flgs} \ast \ulcorner (\textsf{rvd + imm} > 0 \lor \textsf{rvd + imm} = 0 ) \urcorner \ast \arcr

@@

 \end{array}\right\}_{\textsf{rtv}}  \;

@@

  \left\{ \begin{array}{l}
    P \ast \mathcal{I}\textsf{ASpace}\ast \mathcal{I}\textsf{ASpace} \ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{iv + x} \ast \ulcorner x = 3 \lor x =4 \urcorner \ast \arcr
    r_d \mapsto_{r}  \textsf{v} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v}
  \end{array} \right\}_{\textsf{rtv}}\;\overline{is}
